Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support).

### 2017-02-07 csf-2017/paper.tex
lr editing

% Intuition
The logical relation is a semantic model of all the words on the
capability machine that are definitely safe to give to an
adversary. Whether a capability is safe to give to an adversary
depends heavily on the contents of the memory since instructions as well
as capabilities may reside in memory. The memory will be modeled using
worlds. A world consists of a finite set of regions, and each region
can be understood as a protocol describing the possible evolution of
part of the memory. Memory changes during an
execution since new memory can be allocated and part of the existing
memory can change. We use two future world relations to capture
such changes to the memory in our model.
%

\subsection{Worlds}
\todo[inline]{Find a good place to describe monotonicity of
  interpretation function.}
% Intuition worlds
The worlds are step-indexed Kripke worlds. For the reader not familiar
with these, it is sufficient to think of worlds as finite sets of
regions that impose protocols on the memory.

% Regions intuition
We have three types of regions: $\perma$, $\temp$, and $\revoked$. The
$\perma$ and $\temp$ regions contains a state transition system with
public and private transitions as known from logical relations
from high-level languages\todo{reference}. The state transition
systems can be understood as protocols the memory must follow. The
protocols imposed on memory by $\perma$ regions stay in place
indefinitely. This means that any capability, $\local$ or $\glob$, can
depend on these protocols. The protocols imposed on memory by $\temp$
regions can be revoked at certain points during execution
corresponding to the points when $\local$ capabilities can be
revoked. This means that $\local$ capabilties safely can depend on the
protocols imposed on memory by $\temp$ regions, but $\glob$
capabilities cannot as the $\glob$ capability may stay around
throughout the execution of a program, but the $\temp$ regions may not
stay around.

For monotonicity reasons, a region cannot disappear, but
we need a way to remove $\temp$ regions. This is where the $\revoked$ region comes
into the picture. The $\revoked$ region contains no state transition
system and puts no requirements on the memory it models. It serves
simply as a mask for the $\temp$ regions that have been revoked.

>>>>

% Intuition
The logical relation is a semantic model of all the words on the
capability machine that are definitely safe to give to an
adversary. Whether a capability is safe to give to an adversary
depends heavily on the contents of the memory since instructions as well
as capabilities may reside in memory. Hence we index the logical
relation over worlds, which are used to model the memory, and our logical
relation is thus an example of what is often referred to as a Kripke
logical relation. A world consists of a finite set of regions, and each region
can be understood as a protocol describing the possible evolution of
part of the memory. Memory changes during an
execution since new memory can be allocated and part of the existing
memory can change. We use two future world relations to capture
such changes to the memory in our model.
%

\subsection{Worlds}
\todo[inline]{Find a good place to describe monotonicity of
  interpretation function.}

A world is a finite map from region names, modeled as natural numbers, to regions.
We have three types of regions: \emph{permanent}, \emph{temporary}, and \emph{revoked}.
%$\perma$, $\temp$, and $\revoked$. The
%$\perma$ and $\temp$ 
Each permanent and temporary region contains a state transition system, with
public and private transitions, which describes the protocol governing
the evolution of the memory described by the region, similarly to what
has been used in logical relations for high-level
languages~\cite{Ahmed:popl09,Dreyer:jfp12,Devriese:2016ObjCap}. 
The protocols imposed on memory by permanent regions stay in place
indefinitely. This means that any capability, local or global, can
depend on these protocols. The protocols imposed on memory by temporary
regions can be revoked at certain points during execution,
corresponding to the points when local capabilities can be
revoked. This means that local capabilities safely can depend on the
protocols imposed on memory by temporary regions, wheareas global
capabilities cannot, since a global capability may stay around
throughout the execution of a program, but a temporary region may be
revoked.

For technical reasons (monotonicity of the logical relation), a
temporary region is not removed in the model when it is
revoked. Instead it is turned into a new kind of region, namely a
revoked region. A revoked region contains no state transition
system and puts no requirements on the memory it models. It serves
simply as a mask for a temporary region that have been revoked.
(This way of masking a region goes back to earlier work of
Ahmed~\cite{Ahmed2004semantics} and was also used in~\cite{Thamsborg:2011:KLR:2034773.2034831}.)
